Influence of Connectivity on Dung Beetle Communities

### 2025-04-25 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
some writing

Corridors have been shown to be an important mechanism for facilitating the movement of organisms through fragmented landscapes with the goal of minimizing negative consequences of fragmentation[@haddad_corridor_2003].

@@

All dung beetles were counted and identified to species

>>>>

Corridors have been shown to be an important mechanism for for minimizing negative consequences of fragmentation[@haddad_corridor_2003]. By improving habitat structure to help facilitate dispersal, wildlife corridors inform movement dynamics of local populations and can shape land uses and occupancy (insert richard forman 1995). It is because of this dynamic

@@

All dung beetles were counted and identified to species as described in
